### 2017-08-30 reviews/review1-answers.md

The text in Section Results

```Compression ratio c is an input parameter to the compression algorithm specifying amount of singular values ought to be removed...```

was replaced with the following text:

```In this benchmark, the compression ratio c is an input parameter to the compression algorithm. As follows from the equation (13), the value of compression ratio directly affects the amount of singular values ought to be removed from the SVD decomposition.```

- Line 122: Suggest: summary of sections at the end of Introduction

Following text was added to the end of Introduction:

```The rest of the paper is organized as follows. Section 2 contains math ematical background of the SVD compression (i.e. SVD method itself, its use in low-rank matrix approximation, and description of the randomized SVD method). Implementation of the compression algorithm is presented in Section 3. Section 4 summarizes the results of the benchmarks that were designed to measure quality of the output from the compression algorithm, and also the performance of its the implementation. The paper is concluded in Section 5.```

All other comments were acknowledged and the paper was modified as suggested.

@@

JK:

- We have checked the first paragraph of section 3 but unfortunately we do not understand the source of unclarity. We will be grateful to the reviewer 1 for more detailed comment to this paragraph.

- objection 5 of the reviewer 1: Approximation of the matrix A depends definitely on the number r which is the rank of the approximation of A. 
The higher r, the better approximation. All approximations of A with the rank r are not identical. We are looking for the approximation which is the best one. The quality of approximation can be measured by the probability of incidence of a random vector \tilde{U}\tilde{S}\tilde{V}^Tv in the range of the matrix A, where v denotes a random vector.

- It should be emphasized that Algorithm 1 summarizes a pseudo-code, where the desired approximation is obtained from the full SVD, i.e. the particular singular values with appropriate singular vectors are removed from the factorization and therefore the error NRMSD of the approximation growths.

- line 849: ... it has negligible effect (about ???%, treba 5 %) on the quality ....

- figure 13: We include the columns indicating the full SVD fo Figure 13 in order to show the advantage of randomized SVD and to show the nearly constant computation time for the full SVD.

### 2017-09-03 sections/results.tex
Fix all suggestion of reviewer #3

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/temelin_screenshot}
\caption{Segment of containment analyzed. Results visualization (displacement field, x component).}
\label{fig:temelin:mesh}
\end{figure}

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/temelin_NRMSD}
\caption{Dependence of $\mathit{NRMSD}$ on $c$ for reactor containment analysis results.} % ...$c$ (and $r$)...
\label{fig:temelin:NRMSD}
\end{figure}

% geological layers
Figure \ref{fig:chotkova:mesh} shows results from an analysis of geological layers which was based on theory of plasticity. More details can be found in \cite{Koudelka2006}. This project was chosen mainly to study behavior of compression algorithm when dealing with high discontinuities in data in spatial dimension (as can be seen in visualization). As summarized in Figure \ref{fig:chotkova:NRMSD} and Figure \ref{fig:chotkova:MaxError} this has negligible effect on quality of compression.

@@

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/chotkova_NRMSD}
\caption{Dependence of $\mathit{NRMSD}$ on $c$ for results of geological layers project.}
\label{fig:chotkova:NRMSD}
\end{figure}

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/chotkova_MaxError}
\caption{Dependence of $\mathit{NME}$ on $c$ for results of geological layers project.}
\label{fig:chotkova:MaxError}
\end{figure}

@@

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/mechaxisym_NRMSD}
\caption{Dependence of $\mathit{NRMSD}$ on $c$ for reactor vessel analysis results.}
\label{fig:mechaxisym:NRMSD}
\end{figure}

% PSNR
Figure \ref{fig:PSNR} summarizes the compression error for all three benchmarks using logarithmic scale to make the differences more visible. Peek signal to noise ratio ($\mathit{PSNR}$) metric is used (see Equation (\ref{eq:psnr-def}) for definition). Figure \ref{fig:PSNR_rand} contains the same comparison for the randomized SVD algorithm.

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/PSNR}
\caption{Comparison of $\mathit{PSNR}$ calculated for different decompositions.}
\label{fig:PSNR}
\end{figure}

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/PSNR_rand}
\caption{Comparison of $\mathit{PSNR}$ for different randomized decompositions.}
\label{fig:PSNR_rand}
\end{figure}

@@

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/temelin_ExecutionTime}
\caption{Variation of execution time of standard and randomized SVD calculated for reactor containment analysis results.}
\label{fig:temelin:ExeTime}
\end{figure}

>>>>

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/temelin_screenshot}
\caption{Segment of reactor containment analyzed. Results visualization (displacement field, x component).}
\label{fig:temelin:mesh}
\end{figure}

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/temelin_NRMSD}
\caption{Dependence of $\mathit{NRMSD}$ on $c$ and $r$ for reactor containment analysis results.} % ...$c$ (and $r$)...
\label{fig:temelin:NRMSD}
\end{figure}

% geological layers
Figure \ref{fig:chotkova:mesh} shows results from an analysis of geological layers which was based on theory of plasticity. More details can be found in \cite{Koudelka2006}. This project was chosen mainly to study behavior of compression algorithm when dealing with high discontinuities in data in spatial dimension (as can be seen in visualization). As summarized in Figure \ref{fig:chotkova:NRMSD} and Figure \ref{fig:chotkova:MaxError} this has negligible effect ($\mathit{NRMSD}$ and $\mathit{NME}$ are bellow 1\% even for very small $r$ -- 3 out of 22) on quality of compression.

@@

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/chotkova_NRMSD}
\caption{Dependence of $\mathit{NRMSD}$ on $c$ and $r$ for results of geological layers project.}
\label{fig:chotkova:NRMSD}
\end{figure}

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/chotkova_MaxError}
\caption{Dependence of $\mathit{NME}$ on $c$ and $r$ for results of geological layers project.}
\label{fig:chotkova:MaxError}
\end{figure}

@@

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/mechaxisym_NRMSD}
\caption{Dependence of $\mathit{NRMSD}$ on $c$ and $r$ for reactor vessel analysis results.}
\label{fig:mechaxisym:NRMSD}
\end{figure}

% PSNR
Figure \ref{fig:PSNR} summarizes the compression error for all three benchmarks using $\mathit{PSNR}$ metric. $\mathit{PSNR}$ is defined using logarithm (see Equation (\ref{eq:psnr-def}) for definition), and is included here mainly as a comparison to other image-related compression methods whose quality is often expressed by $\mathit{PSNR}$. Figure \ref{fig:PSNR_rand} contains the same information for the randomized SVD algorithm.

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/PSNR}
\caption{Dependence of $\mathit{PSNR}$ value on $c$ and $r$ calculated for different SVD decompositions.}
\label{fig:PSNR}
\end{figure}

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/PSNR_rand}
\caption{Dependence of $\mathit{PSNR}$ value on $c$ and $r$ calculated for different randomized SVD decompositions.}
\label{fig:PSNR_rand}
\end{figure}

@@

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/temelin_ExecutionTime}
\caption{Variation of execution time of standard and randomized SVD decompositions calculated for reactor containment analysis results.}
\label{fig:temelin:ExeTime}
\end{figure}
